Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2018-01-12 resex.tex
version 2018-01-11

\subsection{Overview of simulations\label{sec:sim}}
For the preparation and interpretation of the experiments two different types of simulations were performed:
\begin{enumerate}
	\item tracking of a Gaussian distribution (Distribution Tracking) to obtain loss rates and emittance growth,
	\item Frequency map analysis (FMA)~\cite{fmalaskar} for the visualization of resonances.
\end{enumerate}
For both simulation types, the tracking code Lifetrac \cite{lifetrac} was used and the simulation parameters are summarized in Table~\ref{tab:sim_param}. Further details on the simulations can be found in \cite{md_sim_hel_res_ex_fitterer,md_sim_hel_res_ex_fitterer_update}.
\begin{table}[b]
	\caption{\label{tab:sim_param}%
		Summary of simulation parameters for the Distribution Tracking and FMA analysis. For details see \cite{md_sim_hel_res_ex_fitterer,md_sim_hel_res_ex_fitterer_update}.
	}
	\begin{ruledtabular}
		\begin{tabular}{lcc}
			Parameter & Distribution Tracking & FMA \\
			\colrule
			beam &\multicolumn{2}{c}{Beam~1} \\
			beam energy &\multicolumn{2}{c}{450 GeV} \\
			emittance & $3.5~\mu$m& $2.5~\mu$m\\
			$4\sigma$ bunch length & \multicolumn{2}{c}{1.3~ns}\\
			$1\sigma$ bunch length & \multicolumn{2}{c}{9.7~cm}\\
			particle & 6D Gaussian & equally spaced grid\\
			distribution &  distribution & in $x,y$ up to $10~\sigma$\\
			&  ($10^4$ particles) & with $\frac{\Delta p}{p_0}=0$\\
			turns tracked & $10^6$ turns & $10^4$ turns \\\hline
			optics & \multicolumn{2}{c}{2016 or 2017 injection optics,}\\
			& \multicolumn{2}{c}{$\beta^*=11$~m}\\
			machine  & standard errors & no errors \\
			imperfections &with $a_1=b_1=a_2=0$\footnote{Orbit errors are disabled due to different implementation of the $a_1,b_1$ errors in Lifetrac and MAD-X. $b_2$ errors are adjusted to yield an average (over 60 seeds) peak $\beta$-beat of 15\% as expected from optics measurements in the LHC.} &  \\
			octupoles  & \multicolumn{2}{c}{$I_{\mathrm{MOF}}=+19.6~\mathrm{A}$, $I_{\mathrm{MOD}}=-19.6~\mathrm{A}$}\\
			tune $(Q_x,Q_y)$ & \multicolumn{2}{c}{(64.28,59.31) for 2016,}\\
			& \multicolumn{2}{c}{(62.27,60.295) for 2017}\\
			chromaticity & \multicolumn{2}{c}{(+15,+15)}\\
			 $(Q'_x,Q'_y)$ & & \\\hline
			 transv. aperture & $5.7~\sigma$ & - \\
			 long. aperture & $10~\sigma$ & - \\
		\end{tabular}
	\end{ruledtabular}
\end{table}

>>>>

\subsection{Overview of simulations\label{sec:sim}}
For the preparation and interpretation of the experiments two different types of simulations were performed:
\begin{enumerate}
	\item tracking of a Gaussian distribution (Distribution Tracking) to obtain loss rates and emittance growth,
	\item Frequency map analysis (FMA)~\cite{fmalaskar} for the visualization of resonances.
\end{enumerate}
For both simulation types, the tracking code Lifetrac \cite{lifetrac} was used and the simulation parameters are summarized in Table~\ref{tab:sim_param}. Further details on the simulations can be found in \cite{md_sim_hel_res_ex_fitterer,md_sim_hel_res_ex_fitterer_update}.
\begin{table}[b]
	\caption{\label{tab:sim_param}%
		Summary of simulation parameters for the Distribution Tracking and FMA analysis. For details see \cite{md_sim_hel_res_ex_fitterer,md_sim_hel_res_ex_fitterer_update}.
	}
	\begin{ruledtabular}
		\begin{tabular}{lcc}
			Parameter & Distribution Tracking & FMA \\
			\colrule
			beam &\multicolumn{2}{c}{Beam~1} \\
			beam energy &\multicolumn{2}{c}{450 GeV} \\
			emittance & $3.5~\mu$m& $2.5~\mu$m\\
			$4\sigma$ bunch length & \multicolumn{2}{c}{1.3~ns}\\
			$1\sigma$ bunch length & \multicolumn{2}{c}{9.7~cm}\\
			particle & 6D Gaussian & equally spaced grid\\
			distribution &  distribution & in $x,y$ up to $10~\sigma$\\
			&  ($10^4$ particles) & with $\frac{\Delta p}{p_0}=0$\\
			turns tracked & $10^6$ turns & $10^4$ turns \\\hline
			optics & \multicolumn{2}{c}{2016 or 2017 injection optics,}\\
			& \multicolumn{2}{c}{$\beta^*=11$~m}\\
			machine  & standard errors & no errors \\
			imperfections &with $a_1=b_1=0$\footnote{Orbit errors are disabled due to different implementation of the $a_1,b_1$ errors in Lifetrac and MAD-X. $b_2$ errors are adjusted to yield an average (over 60 seeds) peak $\beta$-beat of 15\% as expected from optics measurements in the LHC.} &  \\
			octupoles  & \multicolumn{2}{c}{$I_{\mathrm{MOF}}=+19.6~\mathrm{A}$, $I_{\mathrm{MOD}}=-19.6~\mathrm{A}$}\\
			tune $(Q_x,Q_y)$ & \multicolumn{2}{c}{(64.28,59.31) for 2016,}\\
			& \multicolumn{2}{c}{(62.27,60.295) for 2017}\\
			chromaticity & \multicolumn{2}{c}{(+15,+15)}\\
			 $(Q'_x,Q'_y)$ & & \\\hline
			 transv. aperture & $5.7~\sigma$ & - \\
			 long. aperture & $10~\sigma$ & - \\
		\end{tabular}
	\end{ruledtabular}
\end{table}
